---
title: "Setup data for ANNOMI classification examples"
---


Analysis of the Annomi dataset including

- classification of utterances (in context) into questions/reflection etc
- comparison of high and low quality examples 



```{r}
library(BayesFactor)
library(tidyverse)
library(slider)
library(rstanarm)
library(brms)
```


Sets up a new dataset with windows of 4-utterances.
For every utterance:

- take the previous 4 utterances 
- concatenate into `utterance_context`
- select therapist utterances only
- split into test/train sets


```{r}
setwd('soak/data')
df <- read_csv("annomi.csv")

df <- df %>%
  mutate(utterance_full = str_c(interlocutor, ": ", utterance_text, "\\n")) %>%
  group_by(transcript_id) %>%
  mutate(
    context4 = slide_chr(
      utterance_full,
      .f = ~ str_c(.x, collapse = ""),
      .before = 3,     # include previous 3 utterances + current
      .complete = FALSE
    )
  ) %>%
  ungroup() %>% 
  filter(interlocutor=="therapist") %>% 
  filter(!str_detect(context4, "#")) 
  
set.seed(42)
annomi_with_ctx <- df %>%
  # filter(mi_quality=="high") %>% 
  select(transcript_id, interlocutor, mi_quality, utterance_text, utterance_context = context4, question_exists, question_subtype, reflection_exists) %>% 
  mutate(i=runif(n()))

trnscripts_train <- annomi_with_ctx %>% 
  distinct(mi_quality, transcript_id) %>% 
  group_by(mi_quality) %>% 
  slice_head(n=80) %>% 
  pull(transcript_id)

annomi_with_ctx %>% 
  filter(transcript_id %in% trnscripts_train) %>% 
  group_by(mi_quality, transcript_id) %>% 
  slice_head(n=50) %>% 
  arrange(i) %>% 
  glimpse %>% 
  write_csv('annomi_with_ctx_train.csv')
```


# Use soak to classify the inputs

```{bash, eval=F}
# if soak not already installed
uv init
uv add soak-data
uv sync
```


This uses `classifier_tabular.yaml` to categorise all of the contextualised utterances as questions, reflections etc. See below for categories.

```{bash}
uv run soak run soak/pipelines/classifier_tabular.yaml soak/data/annomi_with_ctx_train.csv -o anno10 -F -H 2000 --dump
```


# Results

```{r}
df2 <- read_csv("../../anno10_dump/01_Classifier_classify_utterances/classifications_classify_utterances_a2e6.csv")


df2 %>% glimpse

df2 %>% 
  select(matches('question|reflection|quality')) %>%
  mutate_all(factor) %>%
  pivot_longer(everything()) %>% 
  group_by(name, value) %>% 
  count() %>% 
  group_by(name) %>%
  mutate(p = round(n/sum(n), 2))
```


```{r}
df2 %>% select(question_subtype, question_type) %>% table(., useNA="ifany")
df2 %>% select(reflection, reflection_exists) %>% table(., useNA="ifany")
```




Calculate the reflection/question ratio based on the new LLM classifications:

- `reflection`
- `question_type`

```{r}
rqdf <- df2 %>% 
  group_by(mi_quality, transcript_id) %>% 
    summarise(
      N=n(),
      Q = sum(str_detect('open|closed', question_subtype), na.rm=T), 
      R = sum(str_detect('simple|complex', reflection), na.rm=T)
    ) %>% 
  mutate(RQ = R/Q) %>% 
  filter(RQ<100&RQ>0) %>% 
  mutate(logRQ = log(RQ+.0001))

n_trans <- length(unique(rqdf$transcript_id))
n_ <- length(df2$transcript_id)

rqdf %>% 
  ggplot(aes(RQ, color=mi_quality)) + 
  geom_density() + 
  # geom_density(aes(y = after_stat(count))) +
  # geom_density(aes(y = after_stat(count / sum(count)))) +
  scale_x_log10() + theme_minimal() + labs(color="MI Quality", y="Density", caption=glue::glue("{n_} utterances, from {n_trans} transcripts"))
```


Check if RQ differs between high and low quality examples:

```{r}
1/ttestBF(formula=RQ~mi_quality, data=rqdf)
```


Same test but with more appropropriate model:

```{r}
fit <- stan_glmer.nb(
  R ~ mi_quality + offset(log(Q)) + (1 | transcript_id),
  data = rqdf %>% filter(Q > 0),
  # family = poisson(link = "log")
)
# summary(fit)
exp(fixef(fit))
hypothesis(fit, "exp(mi_qualitylow) < 1") 
```

```{r}
library(broom.mixed)

plotdf <- broom.mixed::tidy(fit, effects = "fixed", conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    OR_low = exp(conf.low),
    OR_high = exp(conf.high)
  )

plotdf %>%
  filter(term != "(Intercept)") %>%  # optional
  ggplot(aes(x = term, y = OR)) +
  geom_pointrange(aes(ymin = OR_low, ymax = OR_high), position = position_dodge(width = 0.5)) +
  geom_hline(yintercept = 1, linetype = 2, colour = "grey50") +
  coord_flip() +
  theme_minimal(base_size = 12) +
  labs(
    y = "Rate ratio (≈ Odds Ratio)",
    x = "",
    title = "Effect of MI quality on reflections per question"
  )

```

```{r}
1/ttestBF(formula = RQ ~ mi_quality, data=rqdf2)
```

```{r}
rqdf %>% 
  # select(-transcript_id) %>% 
  group_by(mi_quality) %>% 
  filter(RQ < Inf & RQ > 0) %>%
  summarise_if(is.numeric, ~median(.x, na.rm=T)) %>% 
  mutate_if(is.numeric, ~round(.x, 3))
```